---
title: "ar_garch_idx"
output: html_document
---

## DJIA,GSPC,NDX,GDAXI,FCHI,SSEC,SENSEX Analysis



```{r}

library(tseries) # Estimate of GARCH through Gaussian (normal)
library(fGarch) # Use for estimation of GARCH model using Student's t distr 

setwd('~/Documents/VaR')

prices <- read.csv('./data/StockIndexData.csv')



```

## DJIA

```{r}

prices.DJIA <- prices[,c('DJIA')]

summary(prices.DJIA)

n <- length(prices.DJIA)
rtn.DJIA <- rep(0,n-1)

for(i in seq(n-1)){
  rtn.DJIA[i] <- log(prices.DJIA[i+1]/prices.DJIA[i]) * 100.
}

```

## Model stock return with AR(1) x GARCH(1,1)

Model AR(1)*GARCH(1,1)

```{r}

rtn.DJIA.ar <- ar(rtn.DJIA, order.max = 1, method = 'ols')

rtn.DJIA.ar

plot(rtn.DJIA.ar$resid,type = 'l')

summary(rtn.DJIA.ar$resid)


rtn.DJIA.ar.resid.garch <- garch(rtn.DJIA.ar$resid[2:length(rtn.DJIA.ar$resid)],trace=FALSE)

rtn.DJIA.ar.resid.garch

plot(rtn.DJIA.ar.resid.garch$residuals,type = 'l')

```

## GSPC

```{r}

prices.GSPC <- prices[,c('GSPC')]

summary(prices.GSPC)

n <- length(prices.GSPC)
rtn.GSPC <- rep(0,n-1)

for(i in seq(n-1)){
  rtn.GSPC[i] <- log(prices.GSPC[i+1]/prices.GSPC[i]) * 100.
}

```

## Model stock return with AR(1) x GARCH(1,1)

Model AR(1)*GARCH(1,1)

```{r}

rtn.GSPC.ar <- ar(rtn.GSPC, order.max = 1, method = 'ols')

rtn.GSPC.ar

plot(rtn.GSPC.ar$resid,type = 'l')

summary(rtn.GSPC.ar$resid)


rtn.GSPC.ar.resid.garch <- garch(rtn.GSPC.ar$resid[2:length(rtn.GSPC.ar$resid)],trace=FALSE)

rtn.GSPC.ar.resid.garch

plot(rtn.GSPC.ar.resid.garch$residuals,type = 'l')

```

## NDX

```{r}

prices.NDX <- prices[,c('NDX')]

summary(prices.NDX)

n <- length(prices.NDX)
rtn.NDX <- rep(0,n-1)

for(i in seq(n-1)){
  rtn.NDX[i] <- log(prices.NDX[i+1]/prices.NDX[i]) * 100.
}

rtn.NDX <- rtn.NDX[!is.na(rtn.NDX)]

```

## Model stock return with AR(1) x GARCH(1,1)

Model AR(1)*GARCH(1,1)

```{r}

rtn.NDX.ar <- ar(rtn.NDX, order.max = 1, method = 'ols')

rtn.NDX.ar

plot(rtn.NDX.ar$resid,type = 'l')

summary(rtn.NDX.ar$resid)


rtn.NDX.ar.resid.garch <- garch(rtn.NDX.ar$resid[2:length(rtn.NDX.ar$resid)],trace=FALSE)

rtn.NDX.ar.resid.garch

plot(rtn.NDX.ar.resid.garch$residuals,type = 'l')

```

## GDAXI

```{r}

prices.GDAXI <- prices[,c('GDAXI')]

summary(prices.GDAXI)

n <- length(prices.GDAXI)
rtn.GDAXI <- rep(0,n-1)

for(i in seq(n-1)){
  rtn.GDAXI[i] <- log(prices.GDAXI[i+1]/prices.GDAXI[i]) * 100.
}

rtn.GDAXI <- rtn.GDAXI[!is.na(rtn.GDAXI)]

```

## Model stock return with AR(1) x GARCH(1,1)

Model AR(1)*GARCH(1,1)

```{r}

rtn.GDAXI.ar <- ar(rtn.GDAXI, order.max = 1, method = 'ols')

rtn.GDAXI.ar

plot(rtn.GDAXI.ar$resid,type = 'l')

summary(rtn.GDAXI.ar$resid)


rtn.GDAXI.ar.resid.garch <- garch(rtn.GDAXI.ar$resid[2:length(rtn.GDAXI.ar$resid)],trace=FALSE)

rtn.GDAXI.ar.resid.garch

plot(rtn.GDAXI.ar.resid.garch$residuals,type = 'l')

```

## FCHI

```{r}

prices.FCHI <- prices[,c('FCHI')]

summary(prices.FCHI)

n <- length(prices.FCHI)
rtn.FCHI <- rep(0,n-1)

for(i in seq(n-1)){
  rtn.FCHI[i] <- log(prices.FCHI[i+1]/prices.FCHI[i]) * 100.
}

rtn.FCHI <- rtn.FCHI[!is.na(rtn.FCHI)]

```

## Model stock return with AR(1) x GARCH(1,1)

Model AR(1)*GARCH(1,1)

```{r}

rtn.FCHI.ar <- ar(rtn.FCHI, order.max = 1, method = 'ols')

rtn.FCHI.ar

plot(rtn.FCHI.ar$resid,type = 'l')

summary(rtn.FCHI.ar$resid)


rtn.FCHI.ar.resid.garch <- garch(rtn.FCHI.ar$resid[2:length(rtn.FCHI.ar$resid)],trace=FALSE)

rtn.FCHI.ar.resid.garch

plot(rtn.FCHI.ar.resid.garch$residuals,type = 'l')

```

## SSEC

```{r}

prices.SSEC <- prices[,c('SSEC')]

summary(prices.SSEC)

n <- length(prices.SSEC)
rtn.SSEC <- rep(0,n-1)

for(i in seq(n-1)){
  rtn.SSEC[i] <- log(prices.SSEC[i+1]/prices.SSEC[i]) * 100.
}

rtn.SSEC <- rtn.SSEC[!is.na(rtn.SSEC)]

```

## Model stock return with AR(1) x GARCH(1,1)

Model AR(1)*GARCH(1,1)

```{r}

rtn.SSEC.ar <- ar(rtn.SSEC, order.max = 1, method = 'ols')

rtn.SSEC.ar

plot(rtn.SSEC.ar$resid,type = 'l')

summary(rtn.SSEC.ar$resid)

rtn.SSEC.ar.resid.garch <- garch(rtn.SSEC.ar$resid[2:length(rtn.SSEC.ar$resid)],trace=FALSE)

rtn.SSEC.ar.resid.garch

plot(rtn.SSEC.ar.resid.garch$residuals,type = 'l')

```

##Model AR(1)*t-GARCH(1,1)

```{r}

gfit.fg <- garchFit(data=rtn.SSEC.ar$resid[2:length(rtn.SSEC.ar$resid)], cond.dist="std")
coef(gfit.fg)
gfit.fg

plot(gfit.fg@residuals, type="l")

```



## SENSEX

```{r}

prices.SENSEX <- prices[,c('SENSEX')]

summary(prices.SENSEX)

n <- length(prices.SENSEX)
rtn.SENSEX <- rep(0,n-1)

for(i in seq(n-1)){
  rtn.SENSEX[i] <- log(prices.SENSEX[i+1]/prices.SENSEX[i]) * 100.
}

rtn.SENSEX <- rtn.SENSEX[!is.na(rtn.SENSEX)]

```

## Model stock return with AR(1) x GARCH(1,1)

Model AR(1)*GARCH(1,1)

```{r}

rtn.SENSEX.ar <- ar(rtn.SENSEX, order.max = 1, method = 'ols')

rtn.SENSEX.ar

plot(rtn.SENSEX.ar$resid,type = 'l')

summary(rtn.SENSEX.ar$resid)


rtn.SENSEX.ar.resid.garch <- garch(rtn.SENSEX.ar$resid[2:length(rtn.SENSEX.ar$resid)],trace=FALSE)

rtn.SENSEX.ar.resid.garch

plot(rtn.SENSEX.ar.resid.garch$residuals,type = 'l')

```



##Model AR(1)*t-GARCH(1,1)

```{r}

gfit.fg <- garchFit(data=rtn.SENSEX.ar$resid[2:length(rtn.SENSEX.ar$resid)], cond.dist="std")
coef(gfit.fg)
gfit.fg

plot(gfit.fg@residuals, type="l")

```
